Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-03 Experiments.tex
removing addressed comments in 5.2

In this experiment  we run as many AthenaMP instances (hereafter referred to
as tasks)  as the number of nodes controlled by the pilot. Each AthenaMP
simulates 100 events, requiring $\sim 4200$ seconds on average. \jhanote{Please
convert all measurements into seconds!}\aanote{Done}

Tasks do not  wait within the NGE Agent's queue since  one node  is available
to each AthenaMP instance.  Overheads in task execution are consequence
primarily of the three other factors: (i) the  initial bootstrapping of the
pilot on the nodes; (ii) the UnitManager's dispatching of  units (tasks) to
the agent; and (iii) time for the agent to initialize all the tasks on the nodes.
\jhanote{"spawn" is the right word here. The agent does not spawn tasks. These
are predefined. I would say "initialize" maybe? Something better?}\aanote{Done. I put initialize, maybe bootstrap would be better?}

@@

% Firstly, w
We % can
observe that, despite some fluctuations due to external factors
% \footnote{such as the
(e.g., Titan's shared filesystem and the shared database used by the NGE), the
average execution time of AthenaMP % oscillates
ranges between 4200 and 4800 seconds. % Secondly, w
We % can
also observe that in all the cases the gap between AthenaMP execution times and
the pilot durations is minimal, although it slightly increases with the pilot
size. % By observing NGE's overhead, w
We % can
notice that NGE's overhead does grow linearly with the number of units.
\jhanote{It does grow linearly with units! What am I missing??}\aanote{Corrected. I think that ``not'' came from a previous version of the sentence. }

>>>>

In this experiment  we run as many AthenaMP instances (hereafter referred to
as tasks)  as the number of nodes controlled by the pilot. Each AthenaMP
simulates 100 events, requiring $\sim 4200$ seconds on average.

Tasks do not  wait within the NGE Agent's queue since  one node  is available
to each AthenaMP instance.  Overheads in task execution are consequence
primarily of the three other factors: (i) the  initial bootstrapping of the
pilot on the nodes; (ii) the UnitManager's dispatching of  units (tasks) to
the agent; and (iii) time for the agent to bootstrap all the tasks on the nodes.

@@

% Firstly, w
We % can
observe that, despite some fluctuations due to external factors
% \footnote{such as the
(e.g., Titan's shared filesystem and the shared database used by the NGE), the
average execution time of AthenaMP % oscillates
ranges between 4200 and 4800 seconds. % Secondly, w
We % can
also observe that in all the cases the gap between AthenaMP execution times and
the pilot durations is minimal, although it slightly increases with the pilot
size. % By observing NGE's overhead, w
We % can
notice that NGE's overhead does grow linearly with the number of units.
